Quality Criteria for SKOS Vocabularies

### 2012-03-20 background.tex
fixed notion of metrics

% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions defining data model consistency. Such quality criteria are already well-established and have extensively been discussed in standardized guidelines [\todo{CM}{ISO refs}], manuals [\todo{CM}{hedden book, skosify ref 3}], and scholarly articles [\todo{cm}{e.g., skosify refs 16/17}].
% TODO: bitte hier einfach nur die referenzen auf die wir uns beziehen zusammenfassen und kategorisieren. Schau dir dazu auch nochmals die SKOSify referenzen und die aus eurem iSemantics paper an.
If we want check existing SKOS vocabularies against these criteria, we first need to identify them and determine how to evaluate them given the syntax, structure and semantics of SKOS. Since we want to provide tool support for quality checking, we must formalize these criteria into computable metrics, in order to ensure consistent implementation and interpretation across tools.

>>>>

% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
Thus, in order to help vocabulary and application designers in judging the quality of SKOS vocabularies, we need higher-level quality criteria that go beyond low-level integrity conditions defining data model consistency. Such quality criteria are already well-established and have extensively been discussed in standardized guidelines [\todo{CM}{ISO refs}], manuals [\todo{CM}{hedden book, skosify ref 3}], and scholarly articles [\todo{cm}{e.g., skosify refs 16/17}].
% TODO: bitte hier einfach nur die referenzen auf die wir uns beziehen zusammenfassen und kategorisieren. Schau dir dazu auch nochmals die SKOSify referenzen und die aus eurem iSemantics paper an.
If we want check existing SKOS vocabularies against these criteria, we first need to identify them and determine how to evaluate them given the syntax, structure and semantics of SKOS. Since we want to provide tool support for quality checking, we must formalize these criteria into computable quality checking functions, in order to ensure consistent implementation and interpretation across tools.
